Journey: A Study in Unhelpful Titles (TODO: should we get a new title?)

### 2017-04-25 paper.tex
Added a bunch of figures

Assume the memory usage of the rest of the system is $R$. We denote $R_i$ as the
$i$-th measurement of $R$ during a run ($i = 0, 1, ... 2^{20}$). System memory
usage is known to jitter in Linux (TODO: cite). To adjust for this jitter, we
define $\Delta_i = R_i - R_0$. For each operation, we take the median value of
$\Delta_i$ across the 5 runs to reduce jitter further.  This is the value
graphed in the figures in this section. $\Delta_i$ represents the increase in
memory usage due to memory management overheads caused by running $i$ memory
management operations.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/mmap_mem_usage}
    \caption{$\Delta_i$ adjusted with control for benchmarks}
\end{figure}

@@

TODO: memory results: SPAI

TODO: time results: HP

@@

TODO: memory: SPAI

TODO: time: HP/MARKM

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_touch_time_cont_cdf}
    \caption{CDF Time to touch a page while swapping for continuous benchmark}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_touch_time_rand_cdf}
    \caption{CDF Time to touch a page while swapping for random benchmark}
\end{figure}

>>>>

Assume the memory usage of the rest of the system is $R$. We denote $R_i$ as the
$i$-th measurement of $R$ during a run ($i = 0, 1, ... 2^{20}$). System memory
usage is known to jitter in Linux (TODO: cite). To adjust for this jitter, we
define $\Delta_i = R_i - R_0$. For each operation, we take the median value of
$\Delta_i$ across the 5 runs to reduce jitter further.  This is the value
graphed in the figures in the following section. $\Delta_i$ represents the
increase in memory usage due to memory management overheads caused by running
$i$ memory management operations.

@@

\subsubsection{Time (TODO: HP)}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/mmap_latency}
    \caption{Latency of memory operations}
\end{figure}

\subsubsection{Memory (TODO: SPAI)}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures/mmap_mem_usage}
    \caption{$\Delta_i$ adjusted with control for benchmarks}
\end{figure}

@@

@@

\subsubsection{Memory (TODO: SPAI)}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_rss}
    \caption{RSS while touching pages while swapping for random benchmark.}
\end{figure}

\subsubsection{Time (TODO: HP/MARKM)}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_touch_time_cont_cdf}
    \caption{CDF of time to touch a page while swapping for continuous
    benchmark. Notice that the y-axis scale is from 99.75\% to 100\%.}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_touch_time_rand_cdf}
    \caption{CDF of time to touch a page while swapping for random benchmark.
    Notice that the y-axis scale is from 93\% to 100\%.}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_time_cont}
    \caption{Time to touch a page while swapping for continuous benchmark.
    Notice that the y-scale is logarithmic.}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_time_rand}
    \caption{Time to touch a page while swapping for random benchmark.}
\end{figure}

This experiment is designed to measure the impact of swapping on memory
operation latency.
